---
title: "this is a sassy distill site"
site: distill::distill_website
---


## Fonts


change the body font to Kiwi Maru


```{r echo=TRUE}
library(sass)
kiwi <- font_google("Kiwi Maru")
as_sass(list(
  list("font-variable" = font_collection(kiwi, "system-ui")),
  list("body{font-family: $font-variable}")
))
```

```{r echo=TRUE}
hachi <- font_google("Hachi Maru Pop")
as_sass(list(
  list("font-variable" = font_collection(hachi, "system-ui")),
  list("h1, 
  d-title h1,
  d-article h1,
  d-article h2,
  d-article h3,
  d-article h4,
  d-article h5,
  d-article h6{font-family: $font-variable}")
))
```


This doesn't work. Trying to use sass to create a CSS variable that can be passed to the root --mono-font variable.

```{r echo=TRUE}
mono <- font_google("Major Mono Display")
as_sass(list(
  # make the variable
  list("font-variable" = font_collection(mono, "system-ui")),
  # make the rule
  list("html{--mono-font: #{$font-variable};}")
))
```

This does seem to generate the right css though?

```{r eval=FALSE}
sass(list(
  list(":root{--mono-default: 'Comic Sans'}")
))
```


::: {.my-color}
This is a link that should be [green](https://pkgs.rstudio.com/rmarkdown/).
:::

This is a <span class="my-color">color</span> word.

## Don't 

### know 

#### why

I waited 'til I saw the sun
I don't know why I didn't come
I left you by the house of fun
Don't know why I didn't come
Don't know why I didn't come
When I saw the break of day
I wished that I could fly away
Instead of kneeling in the sand
Catching tear-drops in my hand
My heart is drenched in wine
But you'll be on my mind forever
Out across the endless sea
I would die in ecstasy
But I'll be a bag of bones
Driving down the road alone
